fsOGTT Pre- and Post-ETI

### 2025-10-06 Christine Chan/EnVision CF/fsOGTT_pre_post_ETI.qmd
fsOGTT longitudinal formatting
fsOGTT air formatting again

ids <- read.csv("./Data_Clean/TV_ETI logitudinal patient list.csv", na.strings = "")

@@

    study_id, gem_id, study, Date, age_visit, sex, origin_race, ethnicity, CFTR,
    pancreatic_status, corrector___4, pre_post, bmi, fev1,
    Diagnosis, Glucose_0:Glucose_180, Insulin_0:Insulin_180,

@@

df$race_ethnicity <- factor(df$race_ethnicity,

@@

    "Hispanic", "Native American", "Black/African American", "Black/African American",
    "Hispanic", "Other/Multiple", "Other/Multiple", "Other/Multiple", "Hispanic", "White", "White"

@@

df$pancreatic_status <- factor(df$pancreatic_status,

@@

    study_id, subject_id, study, date_of_visit, age_at_visit_1, gender,
    race_ethnicity, cf_genotype, cf_pancreatic, ETI, pre_post, average_bmi,
    fev1_percent, group_category, lab_ogtt_fasting, min_10_glucose,
    min_30_glucose, lab_ogtt_1_hour_glucose, min_90_glucose,
    lab_ogtt_2_hour_glucose, min_150_glucose, min_180_glucose,
    min_0_insulin, min_10_insulin, min_30_insulin, min_60_insulin,
    min_90_insulin, min_120_insulin, min_150_insulin, min_180_insulin,
    min_0_c_peptide, min_10_c_peptide, min_30_c_peptide, min_60_c_peptide,
    min_90_c_peptide, min_120_c_peptide, min_150_c_peptide, min_180_c_peptide

@@

    gem_id = subject_id, Date = date_of_visit, age_visit = age_at_visit_1,
    sex = gender, CFTR = cf_genotype, pancreatic_status = cf_pancreatic,
    bmi = average_bmi, fev1 = fev1_percent, Diagnosis = group_category,
    min_0_glucose = lab_ogtt_fasting, min_60_glucose = lab_ogtt_1_hour_glucose,

@@

    ~ paste0("Glucose_", parse_number(.)), min_0_glucose:min_180_glucose

@@

    ~ paste0("Insulin_", parse_number(.)), min_0_insulin:min_180_insulin

@@

    ~ paste0("C.Peptide_", parse_number(.)), min_0_c_peptide:min_180_c_peptide

@@

gem$race_ethnicity <- factor(gem$race_ethnicity,

@@

    "White", "Black/African American", "Asian", "Native American",
    "Hispanic", "Other/Multiple"

@@

gem$CFTR <- factor(gem$CFTR,

@@

    "2184delA/M1101K", "2585delT/G551D", "3849+10kb C>T/F508del",
    "508del/508del", "F508del/1078delA", "f508DEL/1154INStc",
    "F508del/1154insTC", "F508del/1811 + 1634A > G", "F508del/1811+1634>G",
    "F508del/2183delAA->G", "F508del/2183delAA>G", "F508del/2184insA",
    "F508del/2711delT", "F508del/2789+5G>A", "F508del/27895GA",
    "F508del/3659delC", "F508del/3849+10kbC>T", "F508del/394delTT",
    "F508del/5492F", "F508del/A561E", "F508del/E60X",
    "f508del/F508del", "F508del/F508del", "F508del/G542X",
    "F508del/G551D", "F508del/N1303K", "F508del/Q98R",
    "F508del/R1162X", "F508del/R117H 9T", "F508del/R117H 9T/5T",
    "F508del/R553X", "F508del/R709X", "F508del/S492F",
    "F508del/W1282X", "F5o8del/F508del", "G542X/1078delT",
    "G542X/W1089X", "G551D/W846X", "I507del/G551D",
    "N1303K/1154insTC", "N1303K/2789 + 5G > A", "N1303K/2789+5G>A",
    "R117H 5t/G576A and R668C on exon 13", "R117H5t/G576A and R668C on exon 13",
    "V520F/3791delC", "W1089X/S492F", "W1090X/S492F"

@@

    "Other/Other", "Other/Other", "Other/Other", "F508del homozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del homozygous",
    "F508del homozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del heterozygous", "F508del heterozygous", "F508del heterozygous",
    "F508del homozygous", "Other/Other", "Other/Other", "Other/Other",
    "Other/Other", "Other/Other", "Other/Other", "Other/Other", "Other/Other",
    "Other/Other", "Other/Other", "Other/Other", "Other/Other"

@@

gem$pancreatic_status <- factor(gem$pancreatic_status,

@@

gem$Diagnosis <- factor(gem$Diagnosis,

>>>>

ids <- read.csv(
    "./Data_Clean/TV_ETI logitudinal patient list.csv",

@@

        study_id,
        gem_id,
        study,
        Date,
        age_visit,
        sex,
        origin_race,
        ethnicity,
        CFTR,
        pancreatic_status,
        corrector___4,
        pre_post,
        bmi,
        fev1,
        Diagnosis,
        Glucose_0:Glucose_180,
        Insulin_0:Insulin_180,

@@

df$race_ethnicity <- factor(
    df$race_ethnicity,

@@

        "Hispanic",
        "Native American",
        "Black/African American",
        "Black/African American",
        "Hispanic",
        "Other/Multiple",
        "Other/Multiple",
        "Other/Multiple",
        "Hispanic",
        "White",
        "White"

@@

df$pancreatic_status <- factor(
    df$pancreatic_status,

@@

        study_id,
        subject_id,
        study,
        date_of_visit,
        age_at_visit_1,
        gender,
        race_ethnicity,
        cf_genotype,
        cf_pancreatic,
        ETI,
        pre_post,
        average_bmi,
        fev1_percent,
        group_category,
        lab_ogtt_fasting,
        min_10_glucose,
        min_30_glucose,
        lab_ogtt_1_hour_glucose,
        min_90_glucose,
        lab_ogtt_2_hour_glucose,
        min_150_glucose,
        min_180_glucose,
        min_0_insulin,
        min_10_insulin,
        min_30_insulin,
        min_60_insulin,
        min_90_insulin,
        min_120_insulin,
        min_150_insulin,
        min_180_insulin,
        min_0_c_peptide,
        min_10_c_peptide,
        min_30_c_peptide,
        min_60_c_peptide,
        min_90_c_peptide,
        min_120_c_peptide,
        min_150_c_peptide,
        min_180_c_peptide

@@

        gem_id = subject_id,
        Date = date_of_visit,
        age_visit = age_at_visit_1,
        sex = gender,
        CFTR = cf_genotype,
        pancreatic_status = cf_pancreatic,
        bmi = average_bmi,
        fev1 = fev1_percent,
        Diagnosis = group_category,
        min_0_glucose = lab_ogtt_fasting,
        min_60_glucose = lab_ogtt_1_hour_glucose,

@@

        ~ paste0("Glucose_", parse_number(.)),
        min_0_glucose:min_180_glucose

@@

        ~ paste0("Insulin_", parse_number(.)),
        min_0_insulin:min_180_insulin

@@

        ~ paste0("C.Peptide_", parse_number(.)),
        min_0_c_peptide:min_180_c_peptide

@@

gem$race_ethnicity <- factor(
    gem$race_ethnicity,

@@

        "White",
        "Black/African American",
        "Asian",
        "Native American",
        "Hispanic",
        "Other/Multiple"

@@

gem$CFTR <- factor(
    gem$CFTR,

@@

        "2184delA/M1101K",
        "2585delT/G551D",
        "3849+10kb C>T/F508del",
        "508del/508del",
        "F508del/1078delA",
        "f508DEL/1154INStc",
        "F508del/1154insTC",
        "F508del/1811 + 1634A > G",
        "F508del/1811+1634>G",
        "F508del/2183delAA->G",
        "F508del/2183delAA>G",
        "F508del/2184insA",
        "F508del/2711delT",
        "F508del/2789+5G>A",
        "F508del/27895GA",
        "F508del/3659delC",
        "F508del/3849+10kbC>T",
        "F508del/394delTT",
        "F508del/5492F",
        "F508del/A561E",
        "F508del/E60X",
        "f508del/F508del",
        "F508del/F508del",
        "F508del/G542X",
        "F508del/G551D",
        "F508del/N1303K",
        "F508del/Q98R",
        "F508del/R1162X",
        "F508del/R117H 9T",
        "F508del/R117H 9T/5T",
        "F508del/R553X",
        "F508del/R709X",
        "F508del/S492F",
        "F508del/W1282X",
        "F5o8del/F508del",
        "G542X/1078delT",
        "G542X/W1089X",
        "G551D/W846X",
        "I507del/G551D",
        "N1303K/1154insTC",
        "N1303K/2789 + 5G > A",
        "N1303K/2789+5G>A",
        "R117H 5t/G576A and R668C on exon 13",
        "R117H5t/G576A and R668C on exon 13",
        "V520F/3791delC",
        "W1089X/S492F",
        "W1090X/S492F"

@@

        "Other/Other",
        "Other/Other",
        "Other/Other",
        "F508del homozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del homozygous",
        "F508del homozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del heterozygous",
        "F508del homozygous",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other",
        "Other/Other"

@@

gem$pancreatic_status <- factor(
    gem$pancreatic_status,

@@

gem$Diagnosis <- factor(
    gem$Diagnosis,
